Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-19 paper.tex
Redo LOC cuts.
Don't know how  #212 got backed out

As discussed in the \nameref{sec-recombination} section, the time complexity of
Hudson's algorithm is predicted to be
quadratic in the population scaled recombination rate
$\rho = 4 N_e L$ (where $L$ is the length of the genome in units of
recombination distance) by Eq.~\eqref{eqn-hsw-bound}.
Fig.~\ref{fig-ancestry-perf} shows the running time for
simulations with a variety of population size, chromosome
length and sample sizes, and shows this quadratic
prediction is well supported by
observations~\citep[see also][Fig.~2]{kelleher2016efficient}.
We also see that the dependence on $n$ is quite weak,
since increasing sample size 100-fold
only increases run time by a factor of 2 or so. However, the
$\log^2{n}$ factor implied by Eq.~\eqref{eqn-hsw-bound}
(the sum is a harmonic number and can be approximated by $\log{n}$)
is not well supported by observed run times (or numbers of events)
except possibly at very
large values of $\rho$. It therefore appears that a different dependence
on $n$ is required to accurately predict simulation time for a
given $\rho$ and $n$.

>>>>

As discussed in the \nameref{sec-recombination} section, the time complexity of
Hudson's algorithm is predicted to be
quadratic in the population scaled recombination rate
$\rho = 4 N_e L$ (where $L$ is the length of the genome in units of
recombination distance) by Eq.~\eqref{eqn-hsw-bound}.
Fig.~\ref{fig-ancestry-perf} shows the running time for
simulations with a variety of population sizes, chromosome
length and sample sizes, and shows this quadratic
prediction is well supported by
observations~\citep[see also][Fig.~2]{kelleher2016efficient}.
We also see that the dependence on $n$ is quite weak,
since increasing sample size 100-fold
only increases run time by a factor of 2 or so. However, the
$\log^2{n}$ factor implied by Eq.~\eqref{eqn-hsw-bound}
(the sum is a harmonic number and can be approximated by $\log{n}$)
is not well supported by observed run times (or numbers of events)
except possibly at very
large values of $\rho$. It therefore appears that a different dependence
on $n$ is required to accurately predict simulation time for a
given $\rho$ and $n$.
